Tables/Graphs for Article

### 2018-01-09 article/graphics.Rmd
commented out x$Answered
updated model, computed CI for hazard

```{r}
x$Answered <- NA
x$Answered[x$answered == 1] <- "Answered"
x$Answered[x$answered == 0] <- "Unanswered"

@@

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                   contain_unanswered + contain_answered + title_questionmark + 
                   text_contain_punct + text_all_lower + update + prior_effort + day +
                   sqrt(avg_tag_score) + rcs(sqrt(avg_tag_length), 4) + rcs(log10(text_length), 5) +
                   rcs(sqrt(device_length), 5) + rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
model

@@

# ------------------------------------------
# data frame with coefficients, HR and confidence intervals
# SE of all coefficients 
se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7196, 0.0309, 0.2661, 0.7231, 0.1856, 0.8452, 4.1706, 6.8975, 0.0714, 0.9724, 2.3149, 2.3255, 0.4776, 0.7265)

@@

coefficientsdf

>>>>

```{r}
# x$Answered <- NA
# x$Answered[x$answered == 1] <- "Answered"
# x$Answered[x$answered == 0] <- "Unanswered"

@@

```{r}
model <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + 
                    contain_unanswered + contain_answered + title_questionmark + 
                    text_contain_punct + text_all_lower + update + prior_effort + 
                    day + sqrt(avg_tag_score) + rcs(log10(text_length), 5) + 
                    rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + 
                    rcs(sqrt(newline_ratio), 3), 
                   data = x, 
                   x = TRUE, y = TRUE, 
                   surv = TRUE)
model
```

@@

# ------------------------------------------
# data frame with coefficients, HR and confidence intervals
# SE of all coefficients 
se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7204, 0.1856, 0.8452, 4.1705, 6.8973, 0.1062, 0.6381, 2.5243, 0.2496, 2.5575, 7.4036, 10.2644, 0.4776, 0.7266)

@@

# putting CI in percentage form 
options(scipen = 99999)
coefficientsdf$upper_p <- NA; coefficientsdf$lower_p <- NA

upper <- coefficientsdf$upper > 1
coefficientsdf$upper_p[upper == TRUE] <- (coefficientsdf$upper[upper == TRUE] - 1) * 100
coefficientsdf$upper_p[upper == FALSE] <- (1 - coefficientsdf$upper[upper == FALSE]) * 100
coefficientsdf$lower_p[upper == TRUE] <- (coefficientsdf$lower[upper == TRUE] - 1) * 100
coefficientsdf$lower_p[upper == FALSE] <- (1 - coefficientsdf$lower[upper == FALSE]) * 100
